\vspace{1.0cm} \LARGE \bf Structured population models demystify MERS-CoV epidemiology

### 2017-07-10 mers-structure.tex
fixing typo

Let $R_{0}$ be the basic reproductive number ($ 0 < R_{0} < 1$),  and $\omega > 0$ be the a dispersion parameter, then the probability of observing a stuttering chain of size (cluster) $r$ of size $j$ is~\citep{blumberg_inference_2013}
\begin{equation}
Pr(r = j | R_{0}, \omega) = \frac{\Gamma(\omega j+j-1)}{\Gamma(\omega j)\Gamma(j+1)} \frac{(\frac{R_{0}}{\omega})^{j-1}}{(1+\frac{R_{0}}{\omega})^{\omega j+j-1}}.
\label{clusterLikelihood}
\end{equation}

>>>>

Let $R_{0}$ be the basic reproductive number ($ 0 < R_{0} < 1$),  and $\omega > 0$ be the a dispersion parameter, then the probability of observing a stuttering chain (cluster) $r$ of size $j$ is~\citep{blumberg_inference_2013}
\begin{equation}
Pr(r = j | R_{0}, \omega) = \frac{\Gamma(\omega j+j-1)}{\Gamma(\omega j)\Gamma(j+1)} \frac{(\frac{R_{0}}{\omega})^{j-1}}{(1+\frac{R_{0}}{\omega})^{\omega j+j-1}}.
\label{clusterLikelihood}
\end{equation}
